\acknowledgment

First and foremost, I want to thank my advisor, Nathan Jones. Nathan, your unbounded and unwavering support and mentorship is what made this thesis possible. I am so grateful for your unabating patience, commitment, and encouragement throughout my mathematical career, and especially in the last few years, as the path to finishing this work became more winding than expected. I have immensely enjoyed our discussions regarding matters both mathematical and otherwise, and they are something I will always look back on with fond memories. 

I would also like to thank the other members of the Number Theory group at UIC, especially Ramin Takloo-Bighash and Alina Cojocaro, for being formative influences throughout my graduate school career. Ramin, you have always been such a positive, humble, and inclusive leader and I hope to effectuate these traits as I continue my own career. Alina, your passion for Number Theory is unparalleled and inspirational, and I will never forget the kindness you have shown me. Thank you both for being members of this committee and supporting this work and my career.

I am very appreciative of the other members of my committee, James Frietag and Alvaro Lozano-Robledo, as well. Thank you for taking the time to read and provide feedback on this work, all during one of the strangest and craziest years we have witnessed. 

As I move towards completing this chapter in my life, I can't help but reflect on other prominent, positive forces that helped shape who I am today. Thank you to the UIC Mathletes, particularly Sam Shideler and Jonathan Wolf, for all the miles and races that we shared. Thank you to Amit Shaw, one of the most hardworking mathematicians I know, for being a great study partner during my first two years at UIC.

Finally, I would like to thank Alicia Vissuet. I could not have asked for a better life partner. You, Odin and Freya are my greatest motivation and what pushes me to be better. I can't wait to see what is next for us.

% This line is required, but of course replace my initials with yours.
\initials{KV}