\begin{thebibliography}{99}

\bibitem{braujones} J. Brau and N. Jones, \emph{Elliptic curves with $2$-torsion contained in the $3$-torsion field}, to appear in Proc. Amer. Math. Soc.

\bibitem{MAGMA} W. Bosma, J. Cannon and C. Playoust, \emph{The {M}agma algebra system. {I}. {T}he user language}, J. Symbolic Comput. \textbf{24}, no. 3-4, (1997), 235--265.

\bibitem{clozeletal} L. Clozel, M. Harris and R. Taylor, \emph{Automorphy for some $\ell$-adic lifts of automorphic mod $\ell$ Galois representations}, Publ. Math. Inst. Hautes \'{E}tudes Sci. \textbf{108} (2008), 1--181.

\bibitem{cogrjo} A.C. Cojocaru, D. Grant and N. Jones, \emph{One-parameter families of elliptic curves over $\mbq$ with maximal Galois representations}, Proc. Lond. Math. Soc. \textbf{103}, no. 3 (2011), 654--675.

\bibitem{cumminspauli} C.J. Cummins and S. Pauli, \emph{Congruence subgroups of $\PSL(2,\mbz)$ of genus less than or equal to 24}, Exp. Math. \textbf{12}, No. 2 (2003) 243--255.

\bibitem{danielsmorrow} H. Daniels and J. Morrow, \emph{A group theoretic perspective on entanglements of division fields}, preprint.

\bibitem{delignerapoport} P. Deligne and M. Rapoport, \emph{Les sch\'{e}mas de modules de courbes elliptiques}, in Modular Functions of One Variable II, Lecture Notes in Mathematics \textbf{349} (1973) 143--316.

\bibitem{denin1} J. B. Dennin, \emph{Fields of modular functions of genus $0$}, Illinois J. Math. \textbf{15} (1971), 442--455.

\bibitem{denin2} J. B. Dennin, \emph{Subfields of $K(2^n)$ of genus $0$}, Illinois J. Math. \textbf{16} (1972), 502--518.

\bibitem{denin3} J. B. Dennin, \emph{The genus of subfields of $K(p^n)$}, Illinois J. Math. \textbf{18} (1974), 246--264.

\bibitem{dokchitser} T. Dokchitser and V. Dokchitser, \emph{Surjectivity of mod $2^n$ representations of elliptic curves}, Math. Z. \textbf{272} (2012), 961--964.

\bibitem{elkies} N. Elkies, \emph{Elliptic curves with $3$-adic Galois representation surjective mod $3$ but not mod $9$}, preprint.  Available at {\tt{https://arxiv.org/abs/math/0612734}}

\bibitem{jonesconductorbound} N. Jones, \emph{A bound for the conductor of an open subgroup of $GL_2$ associated to an elliptic curve}, Pacific J. Math., to appear.

\bibitem{jones2} N. Jones, \emph{$\GL_2$-representations with maximal image}, Math. Res. Lett. \textbf{22} (2015) no. 3, 803--839.

\bibitem{jonesmcmurdy} N. Jones and K. McMurdy, \emph{Elliptic curves with nonabelian entanglements}, preprint.  Available at {\tt{https://arxiv.org/abs/2008.09087}}

\bibitem{langtrotter} S. Lang and H. Trotter, \emph{Frobenius distribution in $\GL_2$ extensions}, 
Lecture Notes in Math. \textbf{504}, Springer (1976). 

\bibitem{lozanorobledo} A. Lozano-Robledo,  \emph{On the field of definition of p-torsion points on elliptic curves over the rationals}, Math. Annalen \textbf{357}, no. 1 (2013), 279--305.

\bibitem{mazur} B. Mazur, \emph{Rational isogenies of prime degree}, Invent. Math. \textbf{44}, no. 2 (1978), 129--162.

\bibitem{merel} L. Merel, \emph{Bornes pour la torsion des courbes elliptiques sure les corps de nombres}, Invent. Math. \textbf{24}, no. 1 (1996), 437--449.

\bibitem{morrow} J. Morrow, \emph{Composite images of Galois for elliptic curves over Q and entanglement fields}, Math. Comp.
\textbf{88} (2019), no. 319, 2389--2421.

\bibitem{ribet} K. Ribet, \emph{Galois action on division points of Abelian varieties with real multiplications}, Amer. J. Math. \textbf{98}, no. 3 (1976), 751--804.

\bibitem{rousedzb} J. Rouse and D. Zureick-Brown, \emph{Elliptic curves over $\mbq$ and $2$-adic images of Galois}, Research in Number Theory, \textbf{1} (2015).

\bibitem{serre} J-P. Serre,  \emph{Propri\'{e}t\'{e}s galoisiennes des points d'ordre fini des courbes elliptiques}, Invent. Math. \textbf{15} (1972), 259--331.

\bibitem{silverman} J. Silverman, \emph{The arithmetic of elliptic curves}, Springer, New York, 1986.

\bibitem{sutherlandzywina} A. Sutherland and D. Zywina, \emph{Modular curves of prime-power level with infinitely many rational points}, Algebra and Number Theory \textbf{11}, no. 5 (2017), 1199--1229.

\bibitem{taylor} R. Taylor, \emph{Automorphy for some $\ell$-adic lifts of automorphic mod $\ell$ Galois representations II}, Publ. Math. Inst. Hautes \'{E}tudes Sci. \textbf{108} (2008), 183--239.

\bibitem{thompson} J. G. Thompson, \emph{A finiteness theorem for subgroups of $\PSL(2,\mbr)$}, in Proc. Symp. Pure Math. \textbf{37}, 533--555, A.M.S. Publications (1980).

\bibitem{weil} A. Weil, \emph{Sur les fonctions algebriques \`{a} corps de constantes finis}, C. R. Acad. Sci. Paris \textbf{210} (1940) 592--594.

\bibitem{zograf} P. Zograf, \emph{A spectral proof of Rademacher’s conjecture for congruence subgroups of the modular group}, J. Reine Angew. Math. \textbf{414} (1991), 113--116.

\bibitem{zywina} D. Zywina, \emph{On the possible images of the mod $\ell$ representations associated to elliptic curves over $\mbq$}, preprint.  Available at
{\tt{https://arxiv.org/abs/1508.07660}}

\bibitem{zywinaindex} D. Zywina, \emph{Possible indices for the Galois image of elliptic curves over $\mbq$}, preprint.  Available at {\tt{https://arxiv.org/abs/1508.07663}}

\end{thebibliography}